API design for machine learning software: experiences from the scikit-learn project

### 2013-10-18 paper.tex
copyedit intro again
I don't think they really do abstracts in CiSE.

{\bf Abstract}
\sklearn is a machine learning library for the Python language.\footnote{\url{http://scikit-learn.org}}
It is designed to be simple and efficient, accessible to
non-experts, and reusable in various contexts. In this article, we present and
discuss the uniform application programming interface shared
by all learning and processing units in the library,
and the way it facilitates composition and reusability. We also comment on
implementation details specific to the Python ecosystem
and analyze potential obstacles faced by users and developers of the library.

@@

Since 2007, \sklearn has been developed by more than a dozen
core developers, mostly researchers in various fields
(among others, computer science, neuroscience, astrophysics). It also benefits
from occasional contributors proposing small bugfixes or
improvements. Development proceeds on GitHub\footnote{\url{https://github.com/scikit-learn}},
a platform which greatly facilitates this kind of
collaboration. Because of the large number of developers, emphasis is
put on keeping the project maintainable. In particular, code must follow
specific quality guidelines, such as style consistency and unit-test coverage.
Documentation and examples are required for all features,
and major changes must pass code review by at least two other
developers.

>>>>

\sklearn is a machine learning library for the Python language.\footnote{\url{http://scikit-learn.org}}
It is designed to be simple and efficient, accessible to
non-experts, and reusable in various contexts. In this article, we present and
discuss the uniform application programming interface shared
by all learning and processing units in the library,
and the way it facilitates composition and reusability. We also comment on
implementation details specific to the Python ecosystem
and analyze potential obstacles faced by users and developers of the library.

@@

Since 2007, \sklearn has been developed by more than a dozen
core developers, mostly researchers in fields ranging from
neuroscience to astrophysics. It also benefits
from occasional contributors proposing small bugfixes or
improvements. Development proceeds on GitHub\footnote{\url{https://github.com/scikit-learn}},
a platform which greatly facilitates this kind of
collaboration. Because of the large number of developers, emphasis is
put on keeping the project maintainable. In particular, code must follow
specific quality guidelines, such as style consistency and unit-test coverage.
Documentation and examples are required for all features,
and major changes must pass code review by at least two other
developers.
